%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Quantitative Researcher} % Job title
    {Citadel Securities Asia Service Limited} % Organization
    {Hong Kong} % Location
    {Sep. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Develop Index Arbitrage strategies which trades equities, index futures and index ETFs.}
        \item {Leverage different ways of monetizing portfolio to achive optimal PnL.}
        \item {Research on multiple risk models to perform risk control to Index Arbitrage portfolio.}
        \item {Continuously improve the robustness of production trading strategy to miminize operational risks.}
        \item {Analyze strategy performance and improve trading efficiency.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Computer Vision Researcher} % Job title
    {Tencent Mobility Limited} % Organization
    {Hong Kong} % Location
    {Dec. 2015 - Sep. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Develop across-platform CNN inference library in C++ with extreme optimization on x86/64 and ARM architecture. Achieve best performance compared with all open source frameworks.}
        \item {Train and optimize convolutional neural network models for image censoring. Text classification, image classification, object detection, image search and weakly supervised learning are used in this project. Achieve top accuracy among public clouds.}
        \item {Implement high performance backend services using C++. Used in WeChat(around 1 billion users) and Tencent Cloud. Over 100 millions API call per day.}
        \item {Implement a cross-platform library for video, image decoding and encoding in C++.}
        \item {Develop a labeling platform for image multi-class classification task and object detection task.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Researcher Application} % Job title
    {SenseTime Group Ltd.} % Organization
    {Hong Kong} % Location
    {Jun. 2018 - Jan. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implement data mining pipeline using Python, including data cleaning, feature engineering and model training on distributed system.}
        \item {Develop Idle Application prediction SDK in C++ for Android system so that mobile thone can schedule background application cleaning without affecting user experience.}
        \item {Responsible for developing E-Channel Child Detection SDK for Hong Kong Immigration Department.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
